A Flexible Generator of Constrained Global Optimization Test Problems

### 2018-04-29 2018/LeGo/LeGo.tex
Some corrections

For example, one generator for random samples of two-dimensional test functions has been 
described in \cite{Grishagin2015}. %more refs
Another generator (\textit{GKLS generator}) for the functions of arbitrary dimensionality with 
known properties (the number of local minima, the size of their domains of attraction, the global 
minimizer, etc.) has been proposed in \cite{Gaviano2003}.  Application of this generator for 
studying some unconstrained optimization algorithms has been described in \cite{Paulavicius2014,Sergeyev2015}.

The generator GCGen (Global Constrained optimization problem Generator) which allows to 
generate the test global optimization problems with $m$ constraints based on the functions of 
this class has been proposed in \cite{Gergel2017}. In the present paper, the rules, which 
allow formulating the constrained global optimization problems have been proposed so that:
\begin{itemize}
	\item one could control the size of feasible domain with respect to the whole domain of 
the parameters' variation;
	\item the global minimizer of the objective function would be known a priori taking into 
account the constraints;
	\item the global minimizer of the objective function without accounting for the 
constraints would be out of the feasible domain.
\end{itemize}

@@

The shifting of the conditional minimum to the boundary of the feasible domain is performed in 
the following way.
\begin{enumerate}
\item A problem with an arbitrary location of the constrained minimum $\overline{y}$ is 
generated;
\item From the point $\overline{y}$, a coordinate search of a feasible point $y^*$, for which at 
least one constraint is active i.e. there is such index $j, 1 \leq j\leq m$ that $\left|g_j(y^*)\right| 
\leq \delta$ is performed with given step $h$. 
\item A rough estimate of $y^*$ obtained is refined by a local method. 
\item The coordinate transformation transferring the point $\overline{y}$ to the point $y^*$ is 
performed. This way, the objective function reaches its minimum at the boundary of feasible 
domain. 
\end{enumerate}

@@

In the case, when it is necessary to generate a problem with a predefined number of active 
constraints $S$ in the constrained minimum point, the rules are modified as follows.
\begin{enumerate}
\item A problem with an arbitrary location of a conditional minimum $\overline{y}$ is 
generated;
\item From the point $\overline{y}$, a coordinate search of a feasible point $y^*$, for which at 
least one constraint is active i. e. there is such index $j, 1 \leq j\leq m$ that $\left|g_j(y^*)\right| 
\leq \delta$ is performed with a predefined step $h$.
\item A rough estimate $y^*$ obtained is refined by a local method. 
\item The number $K$ of the constraints active at the point $y^*$ is determined.
\item If $K>S$, $K-S$ constraints are selected from the set of active constraints, and these ones 
are set to be inactive by subtracting a positive parameter $q$ from the right hand side.
\item If $K<S$, $S-K$ constraints are selected from the set of the inactive ones, and and these 
ones are set to be the active by adding a positive parameter $q$ to the right hand side.
\item The coordinate transformation transferring the point $\overline{y}$ to the point $y^*$ is 
performed. This way, the objective function reaches its minimum at the boundary of the feasible 
domain with the predefined number of active constraints. 
\end{enumerate}

@@

As an illustration, the level lines of the objective functions and the zero-level lines of four 
constraints for the problem constructed on the base of functions from \cite{Grishagin2015} with the volume 
fraction of the feasible domains $\Delta = 0.5$ are shown in Fig.~\ref{fig:VAG}. The feasible 
domains are highlighted by green.

@@

\begin{enumerate}[label=(\alph*)]
	\item The problem has been generated with the constrained optimizer located inside the 
feasible domain.
\item A modification of the problem from item (a): unconstrained optimizer is located outside 
the feasible domain.
\item A modification of the problem from item (b): constrained optimizer is located at the 
boundary of the feasible domain, the number of active constraints is not defined.
\item A modification of the problem from item (c): the number of active constraints is defined 
to be two.
\end{enumerate}

@@

This paper considers the method for generating the global optimization test problems with non-
convex constraints, which allows:
\begin{itemize}
	\item controlling the size of the feasible domain with respect to the whole domain of the 
parameters' variation;
	\item knowing \textit{a priori} the conditional global minimizer of the objective 
function;
	\item generating the unconditional global minimizer of the objective function out of the 
feasible domain;
	\item generating the problems with a conditional minimum point located at the boundary 
of the feasible domain;
	\item defining the number of constraints active at the optimum point.
\end{itemize}

The demonstration of the developed approach in application to well-known index method for 
solving complex multiextremal optimization problems with non-convex constraints is 
considered.

The developed approach allows generating any number of test global optimization problems 
with non-convex constraints for performing multiple computational experiments in order to 
obtain a reliable evaluation of the efficiency of the developed optimization algorithms.

>>>>

A generator for random samples of two-dimensional test functions has been 
described, for example, in \cite{Grishagin1997,Grishagin2015}. %more refs
Another generator (\textit{GKLS generator}) for the functions of arbitrary dimensionality with 
known properties (the number of local minima, the size of their domains of attraction, the global 
minimizer, etc.) has been proposed in \cite{Gaviano2003}.  Application of this generator for 
studying some unconstrained optimization algorithms has been described in \cite{Paulavicius2014,Sergeyev2015}.

The generator GCGen (Global Constrained optimization problem Generator) which allows to 
generate the test global optimization problems with $m$ constraints has been proposed in \cite{Gergel2017}. In this paper, the rules, which allow formulating the constrained global optimization problems have been proposed so that:
\begin{itemize}
	\item one could control the size of feasible domain with respect to the whole domain of 
the parameters' variation;
	\item the global minimizer of the objective function would be known a priori taking into 
account the constraints;
	\item the global minimizer of the objective function without accounting for the 
constraints would be out of the feasible domain.
\end{itemize}

@@

The shifting of the conditional minimum to the boundary of the feasible domain is performed in 
the following way.
\begin{enumerate}
\item A problem with an arbitrary location of the constrained minimum $\overline{y}$ is 
generated;
\item From the point $\overline{y}$, a coordinate search of a feasible point $y^*$, for which at 
least one constraint is active (i.e. there is such index $j, 1 \leq j\leq m$ that $\left|g_j(y^*)\right| 
\leq \delta$) is performed with given step $h$. 
\item A rough estimate of $y^*$ obtained is refined by a local method. 
\item The coordinate transformation transferring the point $\overline{y}$ to the point $y^*$ is 
performed. This way, the objective function reaches its minimum at the boundary of feasible 
domain. 
\end{enumerate}

@@

In the case, when it is necessary to generate a problem with a predefined number of active 
constraints $S$ in the minimizer, the rules are modified as follows.
\begin{enumerate}
\item A problem with an arbitrary location of a conditional minimum $\overline{y}$ is 
generated;
\item From the point $\overline{y}$, a coordinate search of a feasible point $y^*$, for which at 
least one constraint is active i. e. there is such index $j, 1 \leq j\leq m$ that $\left|g_j(y^*)\right| 
\leq \delta$ is performed with a predefined step $h$.
\item A rough estimate $y^*$ obtained is refined by a local method. 
\item The number $K$ of the constraints active at the point $y^*$ is determined.
\item If $K>S$, $K-S$ constraints are selected from the set of active constraints, and these ones 
are set to be inactive by subtracting a positive parameter $q$ from the right hand side.
\item If $K<S$, $S-K$ constraints are selected from the set of the inactive ones, and and these 
ones are set to be the active by adding a positive parameter $q$ to the right hand side.
\item The coordinate transformation transferring the point $\overline{y}$ to the point $y^*$ is 
performed. This way, the objective function reaches its minimum at the boundary of the feasible 
domain with the predefined number of active constraints. 
\end{enumerate}

@@

As an illustration, the level lines of the objective functions and the zero-level lines of three 
constraints for the problem constructed on the base of functions from \cite{Grishagin2015} with the volume 
fraction of the feasible domains $\Delta = 0.5$ are shown in Fig.~\ref{fig:VAG}. The feasible 
domains are highlighted by green.

@@

\begin{enumerate}[label=(\alph*)]
	\item The problem has been generated with the constrained optimizer located inside the 
feasible domain.
\item A modification of the problem from item (a): unconstrained optimizer is located outside 
the feasible domain.
\item A modification of the problem from item (b): constrained optimizer is located at the 
boundary of the feasible domain, the number of active constraints is not predefined.
\item A modification of the problem from item (c): the number of active constraints is defined 
to be two.
\end{enumerate}

@@

This paper considers the method for generating the global optimization test problems with non-
convex constraints, which allows:
\begin{itemize}
	\item controlling the size of the feasible domain with respect to the whole domain of the 
parameters' variation;
	\item knowing a priori the conditional global minimizer of the objective 
function;
	\item generating the unconditional global minimizer of the objective function out of the 
feasible domain;
	\item generating the problems with a conditional minimizer located at the boundary 
of the feasible domain;
	\item defining the number of constraints active at the optimum point.
\end{itemize}

The developed approach allows generating any number of test global optimization problems 
with non-convex constraints for performing computational experiments in order to 
obtain a reliable evaluation of the efficiency of the developed optimization algorithms.
